Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?

### 2018-09-16 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update data section of paper

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for their helpful comments, guidance and suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au"
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different from the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard, and one of Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly, significant events can alter the course of a government. For instance, consider the change in the Howard government after the 9/11 attacks or the 2002 Bali bombings. However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party? And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?

In this paper we use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to model the topics of discussion in Australian parliaments. The advantage of this model is that it allows for topics to be correlated between sitting days, which then allows us to test for changes in topics at various events. The events that we focus on are changes in: 1) government; 2) the political environment (as defined by polling or other results); 3) economic conditions; and 4) the significant events (such as the 9/11 attacks or the Bali Bombings).

We find [INSERT RESULTS]. We also explored the other direction (the impact of what was said in parliaments on events) but it was difficult to find significant effects.

Our work fits into [WHATEVER IT FITS INTO]. While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and hence can identify patterns that may otherwise be overlooked.

@@

# Data
Following the example of the UK a text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^1] Hansard records are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier. For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015. In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990, and @Willis2017 examined how politicians understood climate change. In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.

Australian Hansard records have been analysed for various purposes, but usually not at scale. For instance, @Rasiah2010 examines Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. @GansLeigh2012 examined Australian Hansard records by hand to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.

[^1]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes. For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis. @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians. Both these findings provide reassurance that differences between Hansard and a verbatim record would not be meaningful for this paper.

The Australian parliaments generally make their Hansard records available online as PDFs that can be downloaded. The Federal parliament additionally makes XML records available for years between 1901 and 1980 as well as from 1997. There are roughly 65,000 **(UPDATE)** hansard records available across the chambers of the state and federal parliaments (Table 1) **(UPDATE NUMBERING)**. As with any larger-scale data process, there are many issues with this dataset of PDFs and the known ones are detailed in the Appendix.

| Parliament | House | Years used | Notes |
|:------|-----:|---------:|------:|
| Commonwealth | House of Representatives | 1901 - 2017 | - |
| Queensland | ? | 1861 - 2017 | - |
| New South Wales | ? | ? - 2017 | - |
| Victoria | ? | ? - 2017 | - |
| Tasmania | ? | ? - 2017 | - |
| South Australia | ? | ? - 2017 | - |
| Western Australia | ? | ? - 2017 | - |

The PDFs were processed using the \texttt{PDFtools} R package of @Ooms2018pdftools. A small proportion of the Hansard records had not been put through a professional OCR process and although the Google Tesseract engine as implemented by @Ooms2018tesseract provided some useful data, these were not used in this analysis.

to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS]. The result is a

@@

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au"
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different from the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard and then one of Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government. However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.

In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days. We then construct a **[XYZ]** model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).

We find **[INSERT RESULTS]**.

Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments. A forecasting model is then used to construct a counterfactual. Our work fits into a growing literature that considers text as a input to more usual quantitative techniques, rather than requiring separate analysis. While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.

@@

# Data
## Parliamentary text data
Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Hansard records and their equivalents are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier. For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015 and @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada. In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990 and @PetersonSpirling2018 examined polarisation. In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950. And in the US @GentzkowShapiroTaddy2018 examine congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.

[^Verbatimfootnote]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes. For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis. @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians.

Australian Hansard records have been analysed for various purposes, but usually not at larger-scale. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**. As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in the Appendix.

[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (http://historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980. Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through today from Open Australia’s website.

| Parliament       | House                    | Years used | Number of records |
|:------|-----:|---------:|------:|
| Commonwealth      | House of Representatives | 1901 - 2017 | 7,873 |
|                   | Senate                   | 1901 - 2017 | **[TBD]** |
| Queensland        | Legislative Assembly     | 1860 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1860 - 1922 | **[TBD]** |
| New South Wales[^2]   | Legislative Assembly     | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council     | 1856 - 2017 | **[TBD]** |
| Victoria          | Legislative Assembly     | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1851 - 2017 | **[TBD]** |
| Tasmania[^3]      | House of Assembly        | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1856 - 2017 | **[TBD]** |
| South Australia[^4] | House of Assembly       | 1857 - 2017 | **[TBD]** |
|                   | Legislative Council       | 1840 - 2017 | **[TBD]** |
| Western Australia[^5] | Legislative Assembly  | 1890 - 2017 | **[TBD]** |
|                   | Legislative Council       | 1832 - 2017 | **[TBD]** |

[^2]: The NSW Legislative Council was established earlier than 1856, however the earlier Hansard records have not been through an independent OCR process and were not used in this paper. However, the Google Tesseract OCR engine as implemented by @Ooms2018tesseract provided useful data and these could be used in the future.

[^3]: **[Update this, depending on final Tassie records]**.

[^4]: **[Update this, depending on final SA records]**.

[^5]: **[Update this, depending on final WA records]**.

The formatting of the Hansard records changes between the different parliaments and over time. We use R scripts to convert the PDFs into daily text records.[^seeMyScripts] These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018. The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014. Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are fixed when they occur at scale and can be identified.

[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in the Appendix. The full set of scripts are available on request.

**[ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT RECORD?]**

These daily records are the main data used in this paper, however the daily records are also further divided into individual-level records. Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'. Interjections are interesting in their own right, for instance @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs, but do not usually contribute much to defining the topics being discussed that day.

Usually the disaggregation into individual-level records is done by identifying politicians' names in particular patterns. For instance, when the Hansard record is trying to indicate that a person is speaking, as opposed to being mentioned (for more on the political effect of being mentioned see @Alexander2018), often the name is in upper case (e.g. 'Mr WHITLAM' or 'Mr MENZIES'); followed by a dash or colon; or are next to some title within brackets. There is substantial variation in how the person making a statement is identified. Again some error is introduced at this stage because of inconsistencies over time and between the parliaments, as well as the errors introduced during the PDF parsing stage. There is considerable variance but on average each daily record had 250 **[UPDATE]** individual-level records, resulting in roughly 15 million rows **[UPDATE]** across the state and federal parliaments.

## Parliamentary meta data

TALK ABOUT THE ADDITIONAL DATA

In general,

## Topic pre-processing
There is much more on topic modelling in the next section because topics are the main data analysed in this paper, but here we briefly discuss the pre-processing steps  of creating the topics.

records, and clean the records using functions from the \texttt{Tidyverse} R package of @Wickham2017, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS]. The result is a

@@

## Example workflow
Example of the workflow from PDF to text

### 2018-09-16 outputs/docs/events/svm-rmarkdown-article-example.tex
Update data section of paper

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for
their helpful comments, guidance and suggestions. \textbf{Version as
of}: September 15, 2018; \textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }

@@

New governments often go to some trouble to be different from the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by John Howard, and one of Tony
Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
significant events can alter the course of a government. For instance,
consider the change in the Howard government after the 9/11 attacks or
the 2002 Bali bombings. However it is not so clear which events drive
changes in topics, for instance, do they change when the government is
replaced by another of its own party? And which events are temporary,
for instance when an economic crisis abates, do the topics return to
pre-crisis levels?

In this paper we use the Structural Topic Model (STM) of
\citet{RobertsStewartAiroldi2016} to model the topics of discussion in
Australian parliaments. The advantage of this model is that it allows
for topics to be correlated between sitting days, which then allows us
to test for changes in topics at various events. The events that we
focus on are changes in: 1) government; 2) the political environment (as
defined by polling or other results); 3) economic conditions; and 4) the
significant events (such as the 9/11 attacks or the Bali Bombings).

We find {[}INSERT RESULTS{]}. We also explored the other direction (the
impact of what was said in parliaments on events) but it was difficult
to find significant effects.

Our work fits into {[}WHATEVER IT FITS INTO{]}. While using text as data
has well-known shortcomings, it allows larger-scale analysis that would
not be viable using less-automated approaches and hence can identify
patterns that may otherwise be overlooked.

@@

Following the example of the UK a text record called Hansard of what was
said in Australian parliaments has been made available since their
establishment.\footnote{While Hansard is not necessarily verbatim, it is
  considered close enough for text-as-data purposes. For instance,
  \citet{Mollin2008} found that in the case of the UK Hansard the
  differences would only affect specialised linguistic analysis.
  \citet{Edwards2016} examined Australia, New Zealand and the UK, and
  found that changes were usually made by those responsible for creating
  the Hansard record, instead of the parliamentarians. Both these
  findings provide reassurance that differences between Hansard and a
  verbatim record would not be meaningful for this paper.} Hansard
records are an increasingly popular source of data as new methods and
reduced computational costs make larger-scale analysis easier. For
instance, the digitisation of the Canadian Hansard,
\citet{BeelenEtc2017}, allowed \citet{Whyte2017} to examine whether
parliamentary disruptions in Canada increased between 1926 and 2015. In
the UK, \citet{Duthie2016} analysed Hansard records to examine which
politicians made supportive or aggressive statements toward other
politicians between 1979 and 1990, and \citet{Willis2017} examined how
politicians understood climate change. In New Zealand,
\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
and \citet{Graham2016} examined unparliamentary language between 1890
and 1950.

Australian Hansard records have been analysed for various purposes, but
usually not at scale. For instance, \citet{Rasiah2010} examines Hansard
records for the Australian House of Representatives to examine whether
politicians attempted to evade questions about Iraq during February and
March 2003. \citet{GansLeigh2012} examined Australian Hansard records by
hand to associate mentions by politicians of certain public
intellectuals with neutral or positive sentiment.

The Australian parliaments generally make their Hansard records
available online as PDFs that can be downloaded. The Federal parliament
additionally makes XML records available for years between 1901 and 1980
as well as from 1997. There are roughly 65,000 \textbf{(UPDATE)} hansard
records available across the chambers of the state and federal
parliaments (Table 1) \textbf{(UPDATE NUMBERING)}. As with any
larger-scale data process, there are many issues with this dataset of
PDFs and the known ones are detailed in the Appendix.

\begin{longtable}[]{@{}lrrr@{}}
\toprule
Parliament & House & Years used & Notes\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & 1901 - 2017 & -\tabularnewline
Queensland & ? & 1861 - 2017 & -\tabularnewline
New South Wales & ? & ? - 2017 & -\tabularnewline
Victoria & ? & ? - 2017 & -\tabularnewline
Tasmania & ? & ? - 2017 & -\tabularnewline
South Australia & ? & ? - 2017 & -\tabularnewline
Western Australia & ? & ? - 2017 & -\tabularnewline
\bottomrule
\end{longtable}

The PDFs were processed using the \texttt{PDFtools} R package of
\citet{Ooms2018pdftools}. A small proportion of the Hansard records had
not been put through a professional OCR process and although the Google
Tesseract engine as implemented by \citet{Ooms2018tesseract} provided
some useful data, these were not used in this analysis.

to extract these as text-based CSV records, and clean the records using
functions from the \texttt{Tidyverse} R package of
\citet{WickhamHadleyTidyverse}, the \texttt{Tidytext} R package of
\citet{SilgeRobinson2016} and the {[}INSERT OTHERS{]}. The result is a

@@

>>>>

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 16, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }

@@

New governments often go to some trouble to be different from the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by John Howard and then one of
Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
significant events such as the 9/11 attacks or the Great Recession have
often altered the course of a government. However it is not so clear
which events drive changes, for how long these changes persist, and what
was given up due to the change.

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016} to
impose structure such as correlation between days. We then construct a
\textbf{{[}XYZ{]}} model to examine changes at various types of events,
including: changes in government; changes in the political environment
(as defined by polling or other results); changes in economic
conditions; and other significant events (such as the 9/11 attacks or
the Bali bombings).

We find \textbf{{[}INSERT RESULTS{]}}.

Our paper applies a topic model to a dataset of larger-scale
parliamentary text records from multiple Australian parliaments. A
forecasting model is then used to construct a counterfactual. Our work
fits into a growing literature that considers text as a input to more
usual quantitative techniques, rather than requiring separate analysis.
While using text as data has well-known shortcomings, it allows
larger-scale analysis that would not be viable using less-automated
approaches and so it can identify patterns that may otherwise be
overlooked.

@@

\subsection{Parliamentary text data}\label{parliamentary-text-data}

Following the example of the UK a daily text record called Hansard of
what was said in Australian parliaments has been made available since
their establishment.\footnote{While Hansard is not necessarily verbatim,
  it is considered close enough for text-as-data purposes. For instance,
  \citet{Mollin2008} found that in the case of the UK Hansard the
  differences would only affect specialised linguistic analysis.
  \citet{Edwards2016} examined Australia, New Zealand and the UK, and
  found that changes were usually made by those responsible for creating
  the Hansard record, instead of the parliamentarians.} Hansard records
and their equivalents are an increasingly popular source of data as new
methods and reduced computational costs make larger-scale analysis
easier. For instance, the digitisation of the Canadian Hansard,
\citet{BeelenEtc2017}, allowed \citet{Whyte2017} to examine whether
parliamentary disruptions in Canada increased between 1926 and 2015 and
\citet{RheaultCochran2018} to examine ideology and party polarisation in
Britain and Canada. In the UK, \citet{Duthie2016} analysed Hansard
records to examine which politicians made supportive or aggressive
statements toward other politicians between 1979 and 1990 and
\citet{PetersonSpirling2018} examined polarisation. In New Zealand,
\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
and \citet{Graham2016} examined unparliamentary language between 1890
and 1950. And in the US \citet{GentzkowShapiroTaddy2018} examine
congressional speech records from 1873 to 2016 to find that partisanship
has risen in the past few decades.

Australian Hansard records have been analysed for various purposes, but
usually not at larger-scale. For instance, \citet{Rasiah2010} examined
Hansard records for the Australian House of Representatives to examine
whether politicians attempted to evade questions about Iraq during
February and March 2003. And \citet{GansLeigh2012} examined Australian
Hansard records to associate mentions by politicians of certain public
intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
There is a more limited set of XML records available in some
cases.\footnote{Tim Sherratt makes these XML records available as a
  single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through today from Open Australia's website.} There are
65,000 \textbf{{[}UPDATE{]}} Hansard records available across the state
and federal parliaments (Table 1) \textbf{{[}UPDATE NUMBERING{]}}. As
with any larger-scale data process, there are various issues with some
of the PDFs and the known ones are detailed in the Appendix.

\begin{longtable}[]{@{}lrrr@{}}
\toprule
Parliament & House & Years used & Number of records\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & 1901 - 2017 &
7,873\tabularnewline
& Senate & 1901 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Queensland & Legislative Assembly & 1860 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1860 - 1922 & \textbf{{[}TBD{]}}\tabularnewline
New South Wales\footnote{The NSW Legislative Council was established
  earlier than 1856, however the earlier Hansard records have not been
  through an independent OCR process and were not used in this paper.
  However, the Google Tesseract OCR engine as implemented by
  \citet{Ooms2018tesseract} provided useful data and these could be used
  in the future.} & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Victoria & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1851 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Tasmania\footnote{\textbf{{[}Update this, depending on final Tassie
  records{]}}.} & House of Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
South Australia\footnote{\textbf{{[}Update this, depending on final SA
  records{]}}.} & House of Assembly & 1857 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1840 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Western Australia\footnote{\textbf{{[}Update this, depending on final WA
  records{]}}.} & Legislative Assembly & 1890 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1832 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
\bottomrule
\end{longtable}

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in the Appendix. The full set of
  scripts are available on request.} These scripts are primarily based
on: the \texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified.

\textbf{{[}ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT
RECORD?{]}}

These daily records are the main data used in this paper, however the
daily records are also further divided into individual-level records.
Sometimes these are just short interjections or notes that are not
specific to any particular politician, such as `Honourable members
interjecting'. Interjections are interesting in their own right, for
instance \citet{Whyte2017} analysed them in a Canadian context for the
period 1926 to 2015 to find that female MPs were more likely to be
interrupted than male MPs, but do not usually contribute much to
defining the topics being discussed that day.

Usually the disaggregation into individual-level records is done by
identifying politicians' names in particular patterns. For instance,
when the Hansard record is trying to indicate that a person is speaking,
as opposed to being mentioned (for more on the political effect of being
mentioned see \citet{Alexander2018}), often the name is in upper case
(e.g. `Mr WHITLAM' or `Mr MENZIES'); followed by a dash or colon; or are
next to some title within brackets. There is substantial variation in
how the person making a statement is identified. Again some error is
introduced at this stage because of inconsistencies over time and
between the parliaments, as well as the errors introduced during the PDF
parsing stage. There is considerable variance but on average each daily
record had 250 \textbf{{[}UPDATE{]}} individual-level records, resulting
in roughly 15 million rows \textbf{{[}UPDATE{]}} across the state and
federal parliaments.

\subsection{Parliamentary meta data}\label{parliamentary-meta-data}

TALK ABOUT THE ADDITIONAL DATA

In general,

\subsection{Topic pre-processing}\label{topic-pre-processing}

There is much more on topic modelling in the next section because topics
are the main data analysed in this paper, but here we briefly discuss
the pre-processing steps of creating the topics.

records, and clean the records using functions from the
\texttt{Tidyverse} R package of \citet{Wickham2017}, the
\texttt{Tidytext} R package of \citet{SilgeRobinson2016} and the
{[}INSERT OTHERS{]}. The result is a

@@

\subsection{Example workflow}\label{example-workflow}

Example of the workflow from PDF to text
